---
title: "scryr"
output: github_document
---

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

scryr provides R functions to access Scryfall's APIs for 
[catalogs](https://scryfall.com/docs/api/catalogs), 
[sets](https://scryfall.com/docs/api/sets), and 
[card search](https://scryfall.com/docs/api/cards/search).

# Installation

Install scryr from Github with 
[devtools](https://cran.r-project.org/web/packages/devtools/index.html)

```{r eval=FALSE}
# install.packages("devtools")
library(devtools)
install_github("khailper/scryr")
```

# Usage
```{r setup, message = FALSE}
library(tidyverse)
library(scryr)
```
## scry_catalog()
Scryfall catalogs contain each unique value of the catalogs content, returned as
a vector of strings. So, if you wanted every enchantment subtype:
```{r catalog_example}
scry_catalog("enchantment-types")
```

The list of available catalogs can be found with `?scry_catalog`.

## scry_sets()
`scry_sets` can either return a tibble containing the information for all sets
(the default), or `scry_sets("set's three letter")` to get just the information
for that set.
```{r sets_example}
scry_sets("war")
```

## scry_cards()
`scry_cards()` returns a tibble containing cards matching the seach in the 
`query`arguement. So, if we instead of wanting the information about **War of 
the Spark**, we wanted all cards in that set:
```{r cards_example_a}
war_cards <- scry_cards("s:war")
war_cards
```

`scry_cards` also supports more complex searches (the query syntax is available 
at [https://scryfall.com/docs/syntax](https://scryfall.com/docs/syntax)):
```{r cards_example_b}
# all mono-colored creatures in War of the Spark"
scry_cards("set:war t:'creature' c:1") %>% 
  # need to unlist colors so it can be a grouping variable for count
  mutate(colors = unlist(colors),
         colors = fct_relevel(colors, "W", "U", "B", "R", "G")) %>% 
  # getting each color's mana curve
  count(cmc,colors) %>% 
  ggplot(aes(cmc, n, fill = colors)) +
  geom_col() +
  facet_wrap(~colors) + 
  guides(fill = FALSE) + 
  labs(title = "Mana curve by color in War of the Spark",
       subtitle = "mono-colored creatures only",
       x = "Converted mana cost", 
       y = "Number of cards") +
  theme(strip.background = element_blank(), strip.text.x = element_blank()) +
  scale_fill_manual(values = c("W" = "#ffe7b9",
                               "U" = "#0e68ab",
                               "B" = "#150b00",
                               "R" = "#d3202a",
                               "G" = "#00733e"))
  
```


Note: both `scry_sets` and `scry_cards` by default drop columns related 
containing IDs and URIs. This can be overridden with `include_ids = TRUE` and
`include_uris = TRUE`, respectively.

scryr is unofficial Fan Content permitted under the Fan Content Policy. 
Not approved/endorsed by Wizards. Portions of the materials used are property of
Wizards of the Coast. ©Wizards of the Coast LLC.

scryr is not endorsed or supported by Scryfall. Any use of scryr is subject to 
Scryfall's "Use of Scryfall Data" policy at https://scryfall.com/docs/api.

Please note that the 'scryr' project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
