---
title: "Using label functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{using_label_functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=FALSE}
library(scryr)
library(tidyverse)
# dev version needed for themes (as of 2019-06-23)
# devtools::install_github("wilkelab/cowplot")
library(cowplot)
library(gganimate)
```

Let's use `scry_cards` and `label_guilds` to explore the mana curves of each of 
the draft archetypes in *Modern Horizons*. First, let's find all of the common 
and uncommon cards that either are creatures or make tokens.
```{r scry_data}
# Card Search API syntax guide at https://scryfall.com/docs/syntax
creatures <- scry_cards("t:creature s:mh1 r<=u")
token_makers <- scry_cards("o:token -t:creature s:mh1 r<=u -'generous gift'")

cards <- bind_rows(creatures, token_makers)

cards %>% 
  select(name, mana_cost, cmc, colors) %>% 
  head()
```

Now we can use `label_guild` to assign each card to the color pair(s) that can 
use it (we're going to completely ignore the fact that some cards, like
[Throatseeker](https://scryfall.com/card/mh1/110/throatseeker), are clearly 
better in some archetypes than others). By default, `label_guild` requires an
exact match, so [Alpine Guide](https://scryfall.com/card/mh1/117/alpine-guide) 
would return `NA`. We can use `inclusive = TRUE` to instead get 
`list("Boros", "Gruul", "Izzet", "Rakdos")`. Since `colors` is a list column, we 
need to use `purrr::map`.

```{r add_guild}
cards_with_guilds <- cards %>% 
  mutate(color_pair = map(colors, 
                          label_guild, 
                          inclusive = TRUE, 
                          # so tidyr::unnest() will work well later
                          convert_to_list = TRUE))
```

Let's turn `colors` into something more human-readable
```{r color_change}
create_color_label <- function(color_code){
  case_when(
    length(color_code) == 0 ~ "Artifact",
    length(color_code) > 1 ~ "Multicolored",
    identical(color_code, "B") ~ 
      "Black",
    identical(color_code, "G") ~ 
      "Green",
    identical(color_code, "R") ~ 
      "Red",
    identical(color_code, "U") ~ 
      "Blue",
    identical(color_code, "W") ~ 
      "White",
    TRUE ~ NA_character_
  )
}

cards_with_guilds <- mutate(cards_with_guilds,
                            colors = map_chr(colors, create_color_label))
```

With `tidyr::unnest()`, we can replicate each card for each archetype it could 
belong to, making it easier to count by color pair.

```{r cmc_count}
cmc_count <- cards_with_guilds %>% 
  unnest(color_pair, .drop = FALSE) %>% 
  mutate(color_pair = unlist(color_pair)) %>% 
  count(cmc, colors, color_pair)
```

Now we can visualize our data with `gganimate`
```{r viz}
ggplot(cmc_count, aes(cmc, n, fill = colors)) + 
  # black borders so white fill shows up
  geom_col(color = "black") +
  transition_states(color_pair, transition_length = 2, state_length = 5) +
  cowplot::theme_minimal_hgrid() +
  labs(title = "Common and uncommon creatures/token makers in MH1",
       subtitle = "{closest_state}", 
       x = "Converted Mana Cost", 
       y = "Number of Cards",
       fill = "Color")
```

