---
title: "Using label functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{using_label_functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(scryr)
library(tidyverse)
library(gganimate)
```

Let's use `scry_cards` and `label_guilds` to explore the mana curves of each of 
the draft archetypes in *Modern Horizons*. First, let's find all of the common 
and uncommon cards that either are creatures or make tokens.
```{r scry_data}
# Card Search API syntax guide at https://scryfall.com/docs/syntax
creatures <- scry_cards("t:creature s:mh1 r<=u")
token_makers <- scry_cards("o:token -t:creature s:mh1 r<=u -'generous gift'")

cards <- bind_rows(creatures, token_makers)

cards %>% 
  select(name, mana_cost, cmc, colors) %>% 
  head()
```

Now we can use `label_guild` to assign each card to the color pair(s) that can 
use it (we're going to completely ignore the fact that some cards, like
[Throatseeker](https://scryfall.com/card/mh1/110/throatseeker), are clearly 
better in some archetypes than others). By default, `label_guild` requires an
exact match, so [Alpine Guide](https://scryfall.com/card/mh1/117/alpine-guide) 
would return `NA`. We can use `inclusive = TRUE` to instead get 
`list("Boros", "Gruul", "Izzet", "Rakdos")`.

```{r add_guild}
cards_with_guilds <- cards %>% 
  mutate(color_pair = label_guild(colors, inclusive = TRUE))
```

